What do incoming university students believe about open science practices in

### 2022-04-02 analysis/Manuscript.Rmd
minor tweaks pre-submission

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
  - name: Jennifer L. Beaudry
    affiliation: '1,4'
    role:
      - Conceptualization
      - Data curation
      - Formal analysis
      - Investigation
      - Methodology
      - Project administration
      - Validation
      - Visualization
      - Writing - original draft
      - Writing - review & editing
    corresponding: yes
    email: jen.beaudry@flinders.edu.au
    address: Research Development and Support, Flinders University, Bedford Park, SA, 5042
  - name: Matt N. Williams
    affiliation: '2'
    role:
      - Investigation
      - Methodology
      - Validation
      - Writing - original draft
    email: m.n.williams@massey.ac.nz
  - name: Michael C. Philipp
    affiliation: '2'
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Project administration
      - Writing - original draft
    email: m.philipp@massey.ac.nz
  - name: Emily J. Kothe
    affiliation: '3'
    role:
      - Conceptualization
      - Data curation
      - Validation
      - Visualization
      - Writing - review & editing
    email: emily.kothe@deakin.edu.au
affiliation:
  - id: '1'
    institution: Flinders University, Australia
  - id: '2'
    institution: Massey University, New Zealand
  - id: '3'
    institution: Deakin University, Australia
  - id: '4'
    institution: Swinburne University of Technology, Australia
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default
acknowledgement: |
  The idea of this research was conceived at the 2018 UQ Open Science Conference and further developed at the 2019 Society for the Improvement of Psychological Science Unconference, What do first year psychology students think about (open) science?
  Our special thanks to those who contributed to the data collection effort including: Benjamin Le, Katie Gilligan-Lee, Annayah Prosser, Ian Fairholm, Jennie Ferrell, Kait Clark, Catherine Orr, Nick Burns, Rachel Searston, Rachel Stephens, Matthew Thompson, Aaron Drummond, Kathryn McGuigan, and Peter Cannon.
abstract: |
 Background: Understanding students’ naive conceptions about the norms that guide scientific best practice is important so that teachers can adapt to students’ existing understandings.
 Objective: We examined what incoming undergraduate students of psychology believe about reproducibility and open science practices.
 Method: We conducted an online survey with participants who were about to start their first course in psychology at a university (*N* = 239).
 Results: When asked to indicate how a researcher should conduct her study, most students endorsed several open science practices. When asked to estimate the proportion of published psychological studies that follow various open science practices, participants' estimates averaged near 50%. Only 18% of participants reported that they had heard the term "replication crisis".
 Conclusion: Despite media attention about the replication crisis, few incoming psychology students in our sample were familiar with the term. The students were nevertheless in favour of most open science practices, although they appeared to overestimate the prevalence of some of these practices in psychology.
 Teaching Implications: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.
keywords: open science, psychology, teaching, reproducibility, replication
wordcount: (need to update)
bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: no
draft: no
documentclass: apa6
classoption: man
editor_options: 
  chunk_output_type: console
csl: "apa.csl" 
---

@@

Contacts from tertiary institutions in Australia, New Zealand, the UK, and the USA invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics. These contacts were identified via several avenues, including a dedicated session at the Society for the Improvement of Psychological Science 2019 annual conference, a Twitter thread, and through contacts of the research team. We did not have inclusion criteria with respect to country, but most contacts who advertised the study were from the United Kingdom, Australia, or New Zealand.

@@

Interestingly, only `r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% of participants indicated they had heard of "the replication crisis". Most (`r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`%) indicated that they had not heard of the crisis, and `r round(sum(is.na(df$crisis))/length(df$crisis)*100, 0)`% did not respond.

@@

*Note* Responses to the question: \"Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants. We call repeating a study like this a \'replication study\'. At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?\" Responses provided on a visual slider from 0% to 100%.

@@

Although we have interpreted participants' responses to the norm and counternorm items as reflecting  students' personal endorsement of practices, their perceptions of what we might perceive as the "right" answers could have also influenced their responses. Differences between endorsement of norms and counternorms might have also been affected by wording differences between the matched options; for example, the HARKing, information for replicability, and *p*-hacking counternorm items included the phrase "good scientific practice" whereas their matched norm items did not. More broadly, our choices of terminology in constructing items likely affected participants' responses to some degree. For example, the reference to keeping data "protected" in the open data counternorm item may have nudged participants towards endorsing this item because failing to "protect" participants' data might sound irresponsible. Future research could examine the influence of revised language on participants' responses.

We did not investigate the degree to which results differed according to whether or not participants had studied psychology in high school. Interested readers could conduct this comparison using our open data.

@@

@@

knitr::kable(corr,
             caption = "Correlations between Norms and Counternorms with the 95% Confidence Intervals (in Square Brackets) and the Associated p-values",
             digits = 2,
             align = c('lccc'))

@@

<!-- We have a four references that aren't including the urls. Including here so we can add them to the final document.

@@

Vazire, S. (2019). Do we want to be credible or incredible? Association for Interdisciplinary Meta-research & Open Science conference, Melbourne. https://osf.io/thm9a/

>>>>

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
  - name: Jennifer L. Beaudry
    affiliation: '1,4'
    role:
      - Conceptualization
      - Data curation
      - Formal analysis
      - Investigation
      - Methodology
      - Project administration
      - Validation
      - Visualization
      - Writing - original draft
      - Writing - review & editing
    corresponding: yes
    email: jen.beaudry@flinders.edu.au
    address: Research Development and Support, Flinders University, Bedford Park, SA, 5042
  - name: Matt N. Williams
    affiliation: '2'
    role:
      - Investigation
      - Methodology
      - Validation
      - Writing - original draft
    email: m.n.williams@massey.ac.nz
  - name: Michael C. Philipp
    affiliation: '2'
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Project administration
      - Writing - original draft
    email: m.philipp@massey.ac.nz
  - name: Emily J. Kothe
    affiliation: '3'
    role:
      - Conceptualization
      - Data curation
      - Validation
      - Visualization
      - Writing - review & editing
    email: emily.kothe@deakin.edu.au
affiliation:
  - id: '1'
    institution: Flinders University, Australia
  - id: '2'
    institution: Massey University, New Zealand
  - id: '3'
    institution: Deakin University, Australia
  - id: '4'
    institution: Swinburne University of Technology, Australia
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default
acknowledgement: |
  The idea of this research was conceived at the 2018 UQ Open Science Conference and further developed at the 2019 Society for the Improvement of Psychological Science Unconference, What do first year psychology students think about (open) science?
  Our special thanks to those who contributed to the data collection effort including: Benjamin Le, Katie Gilligan-Lee, Annayah Prosser, Ian Fairholm, Jennie Ferrell, Kait Clark, Catherine Orr, Nick Burns, Rachel Searston, Rachel Stephens, Matthew Thompson, Aaron Drummond, Kathryn McGuigan, and Peter Cannon.
abstract: |
 Background: Understanding students’ naive conceptions about the norms that guide scientific best practice is important so that teachers can adapt to students’ existing understandings.
 Objective: We examined what incoming undergraduate students of psychology believe about reproducibility and open science practices.
 Method: We conducted an online survey with participants who were about to start their first course in psychology at a university (*N* = 239).
 Results: When asked to indicate how a researcher should conduct her study, most students endorsed several open science practices. When asked to estimate the proportion of published psychological studies that follow various open science practices, participants' estimates averaged near 50%. Only 18% of participants reported that they had heard the term "replication crisis".
 Conclusion: Despite media attention about the replication crisis, few incoming psychology students in our sample were familiar with the term. The students were nevertheless in favour of most open science practices, although they overestimated the prevalence of some of these practices in psychology.
 Teaching Implications: Teachers of incoming psychology students should not assume pre-existing knowledge about open science or replicability.
keywords: open science, psychology, teaching, reproducibility, replication
wordcount: 3,009
bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: no
draft: no
documentclass: apa6
classoption: man
editor_options: 
  chunk_output_type: console
csl: "apa.csl" 
---

@@

Contacts from tertiary institutions in Australia, New Zealand, the UK, and the USA invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics. These contacts were identified via several avenues: a session at the annual meeting of the Society for the Improvement of Psychological Science (2019), a Twitter thread, and through contacts of the research team. We did not have inclusion criteria with respect to country, but most contacts who advertised the study were from the United Kingdom, Australia, or New Zealand.

@@

Interestingly, only `r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% of participants indicated they had heard of "the replication crisis". Most (`r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`%) indicated that they had not heard of the crisis; `r round(sum(is.na(df$crisis))/length(df$crisis)*100, 0)`% did not respond.

@@

*Note:* Responses to the question: \"Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants. We call repeating a study like this a \'replication study\'. At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?\" Responses provided on a visual slider from 0% to 100%.

@@

Although we have interpreted participants' responses to the norm and counternorm items as reflecting  students' personal endorsement of practices, their perceptions of what we might perceive as the "right" answers could have also influenced their responses. Differences between endorsement of norms and counternorms might have also been affected by wording differences between the matched options; for example, the HARKing, information for replicability, and *p*-hacking counternorm items included the phrase "good scientific practice" whereas their matched norm items did not. More broadly, our choices of terminology in constructing items might have affected participants' responses to some degree. For example, the reference to keeping data "protected" in the open data counternorm item may have nudged participants towards endorsing this item because failing to "protect" participants' data might sound irresponsible. Future research could examine the influence of revised language on participants' responses.

We did not investigate the degree to which results differed according to whether or not participants had studied psychology in high school. Interested readers could conduct this and other comparisons using our open data.

@@

The supplemental materials contain three sets of results and details of the R packages we used in our analyses. In order, the three results are: (1) the correlations between norm and counternorm items; (2) histograms of participants’ prevalence ratings for each of the norms in practice items; and (3) an additional exploratory analysis examining whether the proportion of students who are unaware of the replication crisis differed between psychology and non-psychology majors.

@@

knitr::kable(corr,
             caption = "Correlations between Norms and Counternorms with 95% Confidence Intervals (in Square Brackets) and Associated p-values",
             digits = 2,
             align = c('lccc'))

@@

<!-- We have four references that aren't including the urls. Including here so we can add them to the final document.

Beaudry, J. L., Kaufman, J., Johnstone, T., & Given, L. (2019). Swinburne Open Science Task Force Survey Report. https://osf.io/eczvd/

@@
